Failure Behaviour Analysis of Automated Pond Oxygen Management System: A Qualitative Study

### 2015-02-20 IFIP FTA/manuscript.tex
done

\usepackage{cite}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage[tight,footnotesize]{subfigure}
\usepackage{graphicx}
\usepackage{url}
\graphicspath{{.}{images/}} % declare the path(s) where your graphic files are
\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Efficient Representation of Chain Code with Digits of Unequal Cost}
\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System: a Qualitative Study}

\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2} \and Martin Walker\inst{1}\and Tanzima Azad\inst{3}}
\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Dhaka, Bangladesh\\
\email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, Martin.Walker@hull.ac.uk, azad.tanzima@dbbl.com.bd}
}
\maketitle

>>>>

\usepackage{cite}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage[tight,footnotesize]{subfigure}
\usepackage{graphicx}
\usepackage{url}
\graphicspath{{.}{images/}} % declare the path(s) where your graphic files are
\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Efficient Representation of Chain Code with Digits of Unequal Cost}
\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System: A Qualitative Study}

\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2} \and Martin Walker\inst{1}\and Tanzima Azad\inst{3}}
\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Engineering \& Technology, Dhaka, Bangladesh\\
\email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, Martin.Walker@hull.ac.uk, azad.tanzima@dbbl.com.bd}
}
\maketitle
